Home

### 2021-09-15 analysis/index.Rmd
misc website updates

---
title: "Home"
site: workflowr::wflow_site
output:
  bookdown::html_document2:
    toc: true
editor_options:
  chunk_output_type: console
---

@@

## [Workflow management](workflow.html) {.unnumbered}

This project uses the [`targets`](https://wlandau.github.io/targets/) and [`workflowr`](https://github.com/jdblischak/workflowr) packages for managing the workflow of the project (making sure that the dependencies between computational steps are satisfied). This notebook contains notes on the proposed workflow for
using `targets` and `workflowr`.

@@

### [Assortative mating MR]() {.unnumbered}

@@

### [PC correlation among couples]() {.unnumbered}

>>>>

---
title: "Home"
author: "Jenny Sjaarda"
site: workflowr::wflow_site
output:
  bookdown::html_document2:
    toc: true
editor_options:
  chunk_output_type: console
---

@@

## [Project Workflow Status](status.html) {.unnumbered}

This notebook displays the computational status of the project, that is, whether everything is up to date. Ironically, this is currently the only notebook that must be run manually, so this notebook only displays the status **when the notebook was last executed** and there is no indication whether the project status has changed since then.

This project uses the [`targets`](https://wlandau.github.io/targets/) and [`workflowr`](https://github.com/jdblischak/workflowr) packages for managing the workflow of the project (making sure that the dependencies between computational steps are satisfied).

@@

### [Assortative mating MR](AM_MR_summary.html) {.unnumbered}

@@

### [Assess impact of geography on causal relationships between couples](geographical_impact.html) {.unnumbered}
